### 2020-04-30 README.Rmd
move package loading to set-up chunk

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

@@

```{r draw-gam-figure, dev = "png", fig.height = 6, fig.width = 7, echo = FALSE, fig.show = "hide", message = FALSE}
library('mgcv')
library('gratia')
df <- gamSim(eg = 1, n = 400, verbose = FALSE)
m <- gam(y ~ s(x0) + s(x1) + s(x2) + s(x3), data = df, model = "REML")
draw(m)
```

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
library('mgcv')
library('gratia')
```

@@

```{r draw-gam-figure, dev = "png", fig.height = 6, fig.width = 7, echo = FALSE, fig.show = "hide", message = FALSE}
df <- gamSim(eg = 1, n = 400, verbose = FALSE)
m <- gam(y ~ s(x0) + s(x1) + s(x2) + s(x3), data = df, model = "REML")
draw(m)
```
